### 2023-10-25 generalExploration.Rmd
fix problematics indexing

reproduction <- function(p1,p2,tp,i=NULL){
    stopifnot(p1$community==p2$community)
    traits=ifelse(sample(c(0,1),length(tp$s),replace=T),p1$traits,p2$traits)
    if(!is.null(i))id=as.numeric(i)+1
    print(id)
    list(
         id=as.character(id),
         traits=traits,
         age=0,
         community=p1$community,
         sex=sample(c("F","M"),1),
         repro=FALSE,
         partner=-1
    )
}

@@

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind[[i]])){
            ##ageing
            population[[ind]]$age=population[[ind]]$age+1

@@

        #quickly summarize
        popsum[[time]]=sapply(names(population[lengths(population)>1][1]),function(n)table(sapply(population,"[[",n)))
        size=table(sapply(population,"[[","community"))
        initcomus$size=size
        ##
        plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
        popsize=c(popsize,length(population))
    }
}

>>>>

reproduction <- function(p1,p2,tp,i=NULL){

    stopifnot(p1$community==p2$community)
    traits=ifelse(sample(c(0,1),length(tp$s),replace=T),p1$traits,p2$traits)
    if(!is.null(i))id=as.numeric(i)+1
    print(id)
    list(
         id=as.character(id),
         traits=traits,
         age=0,
         community=p1$community,
         sex=sample(c("F","M"),1),
         repro=FALSE,
         partner=-1
    )
}

@@

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind)){
            ##ageing
            population[[ind]]$age=population[[ind]]$age+1

@@

        #quickly summarize
        popsum[[time]]=sapply(names(population[[1]]),function(n)table(sapply(population,"[[",n)))
        size=table(sapply(population,"[[","community"))
        initcomus$size=size
        ##
        plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
        popsize=c(popsize,length(population))
    }
}
